#Problem 1

```{r}
library(alr4)

data(jevons)

head(jevons)

# Weight versus Age
plot(jevons$Weight~jevons$Age,
     xlab="Age",
     ylab="Average Weight",
     main="Gold Coin Weight vs Age")

# SD versus Age
plot(jevons$SD~jevons$Age,
     xlab="Age",
     ylab="Standard Deviation",
     main="SD vs Age")

# Variance of each age-group mean
Var=jevons$SD^2/jevons$n

# WLS weights
Wts=1/Var

# Weighted least squares model
WLS=lm(Weight~Age,data=jevons,weights=Wts)

summary(WLS)

# Original least squares model
OLS=lm(Weight~Age,data=jevons)

summary(OLS)

# Plot WLS and OLS fitted lines
plot(jevons$Weight~jevons$Age,
     xlab="Age",
     ylab="Average Weight",
     main="WLS and OLS Fits")

abline(WLS)
abline(OLS,col=2)

# prediction for ages 1 through 5
newdata=data.frame(Age=1:5)

predict(WLS,newdata)

# Predicted values and standard errors
fit=predict(WLS,newdata,se.fit=TRUE)

fit$fit
fit$se.fit

# Standard deviation for individual coin
SDnew=jevons$SD

# Prediction standard error for an individual coin
SEpred=sqrt(SDnew^2+fit$se.fit^2)

# Legal minimum coin weight
Legal=7.9379

# Calculate z-scores
z=(Legal-fit$fit)/SEpred

# Probability that an individual coin is below the legal minimum
Prob=pnorm(z)

#predictions and probabilities
data.frame(Age=1:5,
           PredictedWeight=fit$fit,
           SEpred=SEpred,
           Z=z,
           ProbBelowLegal=Prob)
```

#Analysis: The model shows that coin weight decreases by about 0.0238 grams for every one-year increase in age. Compared with ordinary least squares, weighted least squares gives more weight to the age groups with smaller variance, shwoing a less negative slope. The predicted weights at ages 1 and 2 are above the 7.9379 g legal minimum, while ages 3–5 are below it. This suggests that coins are likely to fall below the legal minimum starting at around age 3.



#Problem 2

```{r}

library(alr4)

data(stopping)

head(stopping)

# Scatter plot
plot(stopping$Distance~stopping$Speed,
     xlab="Speed",
     ylab="Stopping Distance",
     main="Stopping Distance vs Speed")

# Original model
M1=lm(Distance~Speed,data=stopping)

summary(M1)

# Square-root transformation of Distance
M2=lm(sqrt(Distance)~Speed,data=stopping)

summary(M2)

# Plot the transformed relationship
plot(sqrt(Distance)~Speed,data=stopping,
     xlab="Speed",
     ylab="Square Root of Stopping Distance",
     main="Square Root of Distance vs Speed")

abline(M2)

```

#The scatterplot shows that stopping distance increases as speed increases, but the relationship is not completely linear and the variability gets larger at higher speeds. A square-root transformation of Distance makes the relationship more linear for OLS. The transformed model shows that stopping distance increases as speed increases. Overall, the square-root transformation provides a better model for estimating stopping distance from speed.


#Problem 3

```{r}

library(alr4)
library(car)

data(MinnLand)

head(MinnLand)
help(MinnLand)


summary(MinnLand)

# Looked at the main relationships
plot(log(acrePrice)~improvements,data=MinnLand)
plot(log(acrePrice)~log(acres),data=MinnLand)
plot(log(acrePrice)~tillable,data=MinnLand)
plot(log(acrePrice)~crpPct,data=MinnLand)
plot(log(acrePrice)~productivity,data=MinnLand)
plot(log(acrePrice)~year,data=MinnLand)


M1=lm(log(acrePrice)~improvements+year+log(acres)+
        tillable+crpPct+productivity,
      data=MinnLand)

summary(M1)


par(mfrow=c(2,2))
plot(M1)
par(mfrow=c(1,1))

# Check individual relationships
avPlots(M1)

# Check for nonconstant variance
ncvTest(M1)
```

#The model shows that land prices are related to several factors, including improvements, year, farm size, tillable land, and productivity. Using log transformations for acrePrice and acres helps make the relationships more appropriate for a linear regression model. Overall, the model provides a way to explain differences in Minnesota land prices based on the characteristics of the land.
